Exploring the Validity Range of PLL Analytical Models

### 2025-06-01 CaseStudies/Example3_2_LimitsoftheTheorySoFar/Report/article/article.qmd
Finishing charts os report.

$$
H(s)=\frac{\theta_\mathrm{fb}}{\theta_R}=\frac{G(s)}{1+G(s)}
$$ {#eq-PLL-closed-loop-transfer-function-initial}

@@

The closed-loop transfer function of the entire system is given by:

@@

```{python}
#| echo: false
#| label: fig-pll-step-response
#| fig-cap: "Closed-loop step response of the designed PLL."
#| fig-align: center

@@

# Criar vetor da entrada (degrau de amplitude 5)
step_amplitude = np.pi
u = np.ones_like(t) * step_amplitude

@@

# Gerar gráfico
plt.figure(figsize=(8, 5))
plt.plot(t_out * 1e6, y_out, label='Step Response')
plt.plot(t_out * 1e6, u, linestyle=':', color='black', label='Step')
plt.axhline(final_value + tol, color='red', linestyle='--', linewidth=0.8, label='±1% Tolerance')
plt.axhline(final_value - tol, color='red', linestyle='--', linewidth=0.8)
plt.axvline(ts_graphical * 1e6, color='green', linestyle='--', linewidth=1.2, label=f'Graphical settling time: {ts_graphical*1e6:.5f} us')
plt.xlabel('Time [us]')
plt.ylabel('Phase [rad]')
plt.title('Step Response with Settling Time (99%)')
plt.grid(True)
plt.legend()
plt.tight_layout()
plt.show()
```

@@

@@

@@

@@

@@

@@

>>>>

$$
H(s)=\frac{\theta_\mathrm{fb}}{\theta_R}=\frac{\omega_\mathrm{fb}}{\omega_R}=\frac{G(s)}{1+G(s)}
$$ {#eq-PLL-closed-loop-transfer-function-initial}

@@

The closed-loop transfer function of the entire system, both in frequency domain and phase domain is given by:

@@

```{python}
#| echo: false
#| label: fig-pll-step-response
#| fig-cap: "Step Response of the Closed-Loop Frequency Transfer Function of the PLL."
#| fig-align: center

@@

# Criar vetor da entrada (degrau de amplitude 5)
step_amplitude = 0.5e6
u = np.ones_like(t) * step_amplitude

@@

# Gerar gráfico
plt.figure(figsize=(8, 5))
plt.plot(t_out * 1e6, y_out, label='Step Response')
plt.plot(t_out * 1e6, u, linestyle=':', color='black', label='Step')
plt.axhline(final_value + tol, color='red', linestyle='--', linewidth=0.8, label='±1% Tolerance')
plt.axhline(final_value - tol, color='red', linestyle='--', linewidth=0.8)
plt.axvline(ts_graphical * 1e6, color='green', linestyle='--', linewidth=1.2, label=f'Graphical settling time: {ts_graphical*1e6:.5f} us')
plt.xlabel('Time [us]')
plt.ylabel('Frequency (Hz)')
plt.grid(True)
plt.legend()
plt.tight_layout()
plt.show()
```

@@

```{python}
#| echo: false
#| label: fig-pll-step-response-1
#| fig-cap: "Closed-loop step response of the designed PLL."
#| fig-align: center

@@

```{python}
#| echo: false
#| label: fig-pll-step-response-2
#| fig-cap: "Closed-loop step response of the designed PLL."
#| fig-align: center

@@

```{python}
#| echo: false
#| label: fig-pll-step-response-3
#| fig-cap: "Closed-loop step response of the designed PLL."
#| fig-align: center

@@

```{python}
#| echo: false
#| label: fig-pll-step-response-4
#| fig-cap: "Closed-loop step response of the designed PLL."
#| fig-align: center

@@

```{python}
#| echo: false
#| label: fig-pll-step-response-5
#| fig-cap: "Closed-loop step response of the designed PLL."
#| fig-align: center

@@

```{python}
#| echo: false
#| label: fig-pll-step-response-6
#| fig-cap: "Closed-loop step response of the designed PLL."
#| fig-align: center
